What is MaxEnt?

### 2015-06-12 ms.tex
working out stuff

To keep things concrete, suppose all of the unknown parameters are positive,
and our prior is an improper uniform distribution:

\begin{eqnarray}
q(\boldsymbol{x}) \propto
\left\{
\begin{array}{lr}
1, & \forall x_i > 0\\
0, & \textnormal{otherwise}.
\end{array}
\right.
\end{eqnarray}

For any distribution $p(\boldsymbol{x})$, the marginal distribution for $F$ is:

\begin{eqnarray}
p(F) &=& \int \delta\left(F - f(\boldsymbol{x})\right)p(\boldsymbol{x}) \, d^n \boldsymbol{x}
\end{eqnarray}

>>>>

For any distribution $p(\boldsymbol{x})$, the marginal distribution for $F$ is:
\begin{eqnarray}
p(F) &=& \int \delta\left(F - f(\boldsymbol{x})\right)p(\boldsymbol{x}) \, d^n \boldsymbol{x}\label{eqn:constraint}
\end{eqnarray}
If $p(F)$ is a specified function, this is an infinite number of expected
value constraints on $p(\xx)$. Therefore the probability distribution
$p(\xx)$ with maximum entropy with respect to $q(\xx)$ that satisfies the
constraint~\ref{eqn:constraint} is:
\begin{eqnarray}
p(\xx) &=& \frac{q(\xx)}{Z}\exp\left[- \right]
\end{eqnarray}

%To keep things concrete, suppose all of the unknown parameters are positive,
%and our prior is an improper uniform distribution:

%\begin{eqnarray}
%q(\boldsymbol{x}) \propto
%\left\{
%\begin{array}{lr}
%1, & \forall x_i > 0\\
%0, & \textnormal{otherwise}.
%\end{array}
%\right.
%\end{eqnarray}
